\documentclass{article}

\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amsfonts}


\author{Zahary Vogel}
\date{\today}
\title{Notes in ECEN 5623}

\begin{document}
\maketitle


\section*{First day stuff}
REal time embedded omponents and systems with linux and rtos 2nd edition, Sam Siewert and John Pratt ISBN: 978-1942270041\\
ebook is the only thing available\\
web page http://ecee.colorado.edu/~ecen5623/\\
and learn\\
GRAD TA Anurag.Azad@colorado.edu\\

Tim Scherr: main interests are Embedded systems design, especially with respect to single board computers.\\


Project exercises:\\
\begin{enumerate}
    \item INvariant LCM schedules
    \item Service Scheduling Feasibility
    \item Threading and REal-Time Synchronization
    \item REal-Time Continous Media
    \item Real-Time Failures
    \item REal-Time Software System Project
\end{enumerate}

HE always wants attendance. Need a clicker by Thursday.\\
Complete Assignments on time. 10\% a day lost, weekly homeworks. Skip/slip day, where you can turn something in a day or two late and still get credit.\\
Also have assessments which include a few quizzes and 2 exams.\\

Course requirements:\\
Each team (of 2) will get a kit.\\
two options, Altera DE1-SoC which can run RTOS linux or FreeRTOS, or the TI TIVA Launchpad, EK-TM4C123GXL which runs FreeRTOS.\\
30\% in class part, homework, exercises, 30\% exams, 10\% quizzes and final project/exam is 30\%.\\

D2L course webpage.

First homework: read syllabus, siewert, CH 1.\\
Due 1/19:
\begin{enumerate}
    \item Do excercises 1-3 at the end of chapter 1 in the text.
    \item Find a partner
\end{enumerate}

15 minute interview with instructor. Second and third weeks, MF 10-11 am and M-Th 1-2 pm. Doodle poll at:
http://doodle.com/poll/mpmcv5knx2b4nqv2.\\


gave some examples of embedded systems.\\

What does it mean to be embedded:\\
A compute node that provides specific services by proccessing inputs and producing required responses.\\
specific services rather than general purpose computing\\
often no direct connection to user i/o\\
contained within a larger system as a sub-system.\\

real time implies it must respond to a request or service by a deadline relative to the request.\\
rate monotonic, look it up, scheduling type. RMS scheduling gives optimal performance of system based on certain assumptions.\\

RMA and DMA(not direct memory access) analysis exist.\\
desgin methods for multi-thread RTOS systems.\\

final project (2-4 peeps) or individual by approval. This makes up assignment 5 and 6.\\

intro over, slides are online.\\

\section*{Integrating Linux into RT systems}


\end{document}
